Self Regulation Ontology Retest Data Report

### 2018-03-13 code/SRO_Report.Rmd
updating based on draft comments

target task: one without hddm variables, has dv's that are easily codable in r, a lot of trials, possibly multiple dependent measures  
method: import raw response data for chosen task for both t1 and t2, calculate dv's for for both t's for different number of trials, calculate retest reliability point estimates for each of these dv's with different trial numbers  
candidates: angling risk task, columbia card task, dietary decision, hierarchical rule, keep track, probabilistic selection, psychological refractory period, two stage decision

```{r warning=FALSE, message=FALSE}
#read t1 data
t1_tbt = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))

t2_tbt = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/threebytwo.csv.gz'), 'rt'))

#get only retest subjects
t1_tbt = t1_tbt[as.character(t1_tbt$worker_id) %in% as.character(test_data$sub_id),]
t2_tbt = t2_tbt[as.character(t2_tbt$worker_id) %in% as.character(retest_data$sub_id),]

#dv's
calc_break_dvs = function(df, breaks=c(seq(0, 440, 10)[c(-1, -45)], 439)){

  df = df %>%
      filter(exp_stage != "practice")

  calc_dvs = function(df){

    df = df %>%
      mutate(correct_shift = lag(correct),
             task_switch_shift = lag(task_switch))

    missed_percent = mean(df$rt == -1)

     df = df %>%
      filter(rt != -1)

     df_correct = df %>%
       filter(correct == "True" & correct_shift == "True")

     dvs = data.frame(acc = mean(ifelse(df$correct == "True",1,0)),
                      avg_rt_error = median(df$rt[df$correct == "False"]),
                      std_rt_error = sd(df$rt[df$correct == "False"]),
                      avg_rt = median(df_correct$rt),
                      std_rt = sd(df_correct$rt),
                      missed_percent = missed_percent)

     cue_switch_cost_rt_df = df_correct %>% group_by(CTI, cue_switch) %>% summarise(cue_switch_cost = median(rt)) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% ungroup() %>% spread(cue_switch,cue_switch_cost) %>% group_by(CTI) %>% summarise(cue_switch_cost_rt = switch-stay)

     dvs$cue_switch_cost_rt_100 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 100]
     dvs$cue_switch_cost_rt_900 = cue_switch_cost_rt_df$cue_switch_cost_rt[cue_switch_cost_rt_df$CTI == 900]

     task_switch_rt = df_correct %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(rt = median(rt)) %>% complete(task_switch, CTI) %>% ungroup() %>% filter(task_switch == T)

     cue_switch_rt = df_correct %>% group_by(CTI, cue_switch) %>% summarise(rt = median(rt)) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")

     dvs$task_switch_cost_rt_100 = task_switch_rt$rt[task_switch_rt$CTI == 100] - cue_switch_rt$rt[cue_switch_rt$CTI == 100]

     dvs$task_switch_cost_rt_900 = task_switch_rt$rt[task_switch_rt$CTI == 900] - cue_switch_rt$rt[cue_switch_rt$CTI == 900]

     cue_switch_cost_acc_df = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1, 0))) %>% complete(cue_switch, CTI) %>% filter(cue_switch %in% c("stay", "switch")) %>% spread(cue_switch, acc) %>% ungroup() %>% group_by(CTI) %>% summarise(cue_switch_cost_acc = switch-stay)

     dvs$cue_switch_cost_acc_100 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 100]
     dvs$cue_switch_cost_acc_900 = cue_switch_cost_acc_df$cue_switch_cost_acc[cue_switch_cost_acc_df$CTI == 900]

     task_switch_acc = df %>% mutate(task_switch = factor(ifelse(grepl("switch",task_switch), T, F))) %>% group_by(CTI, task_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(task_switch, CTI) %>%  ungroup() %>% filter(task_switch == T)

     cue_switch_acc = df %>% group_by(CTI, cue_switch) %>% summarise(acc = mean(ifelse(correct == "True",1,0))) %>% complete(cue_switch, CTI) %>% ungroup() %>% filter(cue_switch == "switch")

     dvs$task_switch_cost_acc_100 = task_switch_acc$acc[task_switch_acc$CTI == 100] - cue_switch_acc$acc[cue_switch_acc$CTI == 100]

     dvs$task_switch_cost_acc_900 = task_switch_acc$acc[task_switch_acc$CTI == 900] - cue_switch_acc$acc[cue_switch_acc$CTI == 900]

    return(dvs)
  }

  out = data.frame()

  for(i in 1:length(breaks)){
    tmp = df[1:breaks[i],]
    dvs = calc_dvs(tmp)
    out = rbind(out, dvs)
  }

  # due to timeout trials exclusion not all subjects might have 360 rows
  # this would lead to na's for later trial breaks
  # first remove these
  # out = out %>% drop_na()

  # then calculate the dv's for the remaining trials
  if(nrow(df)!=440 & nrow(df)%%10 != 0){
    dvs = calc_dvs(df)
    out = rbind(out, dvs)
  }

  #to keep track for later merge
  out$breaks = row.names(out)

  return(out)
}

#get dv's for t1 and t2
t1_dvs = t1_tbt %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

t2_dvs = t2_tbt %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

# merge to get same number of rows for each subject at both time points
hr_merge = merge(t1_dvs, t2_dvs, by = c("sub_id", "breaks"))

# rm(t1_dvs, t2_dvs)

hr_merge = hr_merge %>%
  gather(key, value, -sub_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))

t1_dvs = hr_merge %>%
  filter(time == 1) %>%
  select(-time) %>%
  spread(dv, value)

t2_dvs = hr_merge %>%
  filter(time == 2) %>%
  select(-time) %>%
  spread(dv, value)

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
# trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))), score_icc=rep(NA, length(unique(t1_dvs$breaks))))
trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))), acc_icc=rep(NA, length(unique(t1_dvs$breaks))), avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))))
for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  # trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)

@@

```{r}
rel_df[c(rel_df$dv %in% grep('hierarchical_rule', rel_df$dv, value = TRUE)),]
```

>>>>

Example task: three by two

```{r warning=FALSE, message=FALSE}
trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))

@@

```{r}
rel_df[c(rel_df$dv %in% grep('threebytwo', rel_df$dv, value = TRUE)),]
```
